master thesis

### 2018-04-02 Paper - Latex/Paper - Skizze - v4.tex
Thesis - appendix again

      Strongly parasitic subtrees are, for example, the Apicomplexa, the Nematoda and the Platyhelminthes. 
        For all three, the prediction is at a similar proportion between input values of the states and 
        predicted states. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
        were predicted. The same applies to the chordata, only that these mainly consist of free-living 
        species.

@@

    Phyla (53): \\
    Acanthocephala, Amoebozoa, Apicomplexa, Arthropoda, Ascomycota, Bacillariophyta, Basidiomycota, 
      Brachiopoda, Bryozoa, Chaetognatha, Chlorophyta, Chordata, Chromerida, Chytridiomycota, 
      Ciliophora, Cnidaria, Colponemidia, Ctenophora, Cycliophora, Echinodermata, Entoprocta, 
      Entorrhizomycota, Euglenida, Foraminifera, Gastrotricha, Glomeromycota, Gnathostomulida, 
      Haplosporida, Haptophyta, Hemichordata, Kinorhyncha, Loricifera, Microsporidia, Mollusca, 
      Myzostomida, Nematoda, Nematomorpha, Nemertea, Onychophora, Orthonectida, Phaeophyceae, 
      Picozoa, Placozoa, Platyhelminthes, Porifera, Priapulida, Rhodophyta, Rhombozoa, Rotifera, 
      Streptophyta, Tardigrada, Xanthophyceae \\
    Wobei von Streptophyta -> Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta als
      Phylum im Phylum gefunden und nicht einbezogen wurden und Magnoliophyta als Phylum in 
      Tracheophyta ebenfalls nicht. \\

    %---------------------------------------------------------------------------------------------------
    \subsection{Distribution of Taxa}
      In the tree we can distinguish 28 different taxa in the OTL taxonomic tree. We have all taxa 
        sorted by rank into a table and counted their occurrences as internal nodes and leaf nodes
        (see table \ref{table:taxa}) and plotted them as a diagram (see figure \ref{fig:taxa}).
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\textwidth]{Figures/TaxaTable2.JPG}
      \caption{Distribution of Nodes in Rank-Cathegories}
      \label{fig:taxa}
    \end{figure}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Parasites in Chordata} \label{sec:parasites in chordata}
    We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
    Known parasitic birds belong to the order Sauria. Here we know from Rothschild here that are 
      breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
      got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
      \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
      known as broodparasite and some others. \\
    An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
      concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
      (\textit{Cyprinus carpio})\footnote{
        \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
        {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio};
        Last checked: 22.03.2018.
      }. Since there is hardly any information about free-living, it follows that all siblings are 
      also predicted to be parasitic.

    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
      \caption{Parasites of Phylum: Chordata. \\
        All parasite data of the chordata are mapped into a rough taxonomy (phylum, class, order, 
          family) in order to understand their distribution and affiliation. \\
        The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
          $\rightarrow$ \# predicted parasites). \\
        The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
          green).}
      \label{fig:ChordataParasites}
    \end{figure}

>>>>

      Strongly parasitic subtrees are, for example, the Apicomplexa, the Nematoda and the Platyhelminthes. 
        For all three, the prediction is at a similar proportion between input values of the states and 
        predicted states. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
        were predicted. The same applies to the Chordata, only that these mainly consist of free-living 
        species.

@@

    Phyla (53): \\
    Acanthocephala, Amoebozoa, Apicomplexa, Arthropoda, Ascomycota, Bacillariophyta, Basidiomycota, 
      Brachiopoda, Bryozoa, Chaetognatha, Chlorophyta, Chordata, Chromerida, Chytridiomycota, 
      Ciliophora, Cnidaria, Colponemidia, Ctenophora, Cycliophora, Echinodermata, Entoprocta, 
      Entorrhizomycota, Euglenida, Foraminifera, Gastrotricha, Glomeromycota, Gnathostomulida, 
      Haplosporida, Haptophyta, Hemichordata, Kinorhyncha, Loricifera, Microsporidia, Mollusca, 
      Myzostomida, Nematoda, Nematomorpha, Nemertea, Onychophora, Orthonectida, Phaeophyceae, 
      Picozoa, Placozoa, Platyhelminthes, Porifera, Priapulida, Rhodophyta, Rhombozoa, Rotifera, 
      Streptophyta, Tardigrada, Xanthophyceae.

      Anthocerotophyta, Marchantiophyta, Bryophyta, Tracheophyta were found as phylum in the phylum 
        Streptophyta and Magnoliophyta as phylum in Tracheophyta and thus not included.

    %---------------------------------------------------------------------------------------------------
    \subsection{Distribution of Taxa}
      In the tree we can distinguish 28 different taxa in the OTL taxonomic tree. We sorted all taxa by
        rank into a table, counted their occurrences as internal nodes and leaf nodes (see table 
        \ref{table:taxa}) and plotted them as a diagram (see figure \ref{fig:taxa}).
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\textwidth]{Figures/TaxaTable2.JPG}
      \caption{Distribution of Nodes in Rank-Cathegories}
      \label{fig:taxa}
    \end{figure}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Parasites in Chordata} \label{sec:parasites in chordata}
    We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): 
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild that there are 
      breeding parasites like the cuckoo and clepto-parasites like the skua  \cite{Rothschild1957}. We
      received 6 input parasites from GloBI and got no predictions: A woodpecker - 
      \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
      known as broodparasite and some others.

    An example of the amplification of mistakes are the carp. There is a paper from which GloBI 
      concludes: the Grass carp (\textit{Ctenopharyngodon idella)} has as pathogen the common carp 
      (\textit{Cyprinus carpio})\footnote{
        \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
        {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio};
        Last checked: 22.03.2018.
      }. Since there is hardly any information about free-living, it follows that all siblings are 
      also predicted to be parasitic.

    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
      \caption{Parasites of Phylum: Chordata. \\
        All parasite data of the Chordata is mapped into a rough taxonomy (phylum, class, order, 
          family) in order to understand its distribution and affiliation. \\
        The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
          $\rightarrow$ \# predicted parasites). \\
        The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
          green).}
      \label{fig:ChordataParasites}
    \end{figure}
